On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-10-03 paper2.tex
text corrected and dereddened

\begin{figure*} 
\centering
\includegraphics[width=0.5\textwidth,height=0.305\textheight]{figures/RLF_LOFAR.eps}
\includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/RLF_LOFAR_analytical_1.eps}
\includegraphics[width=0.5\textwidth,height=0.305\textheight]{figures/CumDensityL_LOFAR.eps}
\includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/CumDensityL_LOFAR_1.eps}
\caption{RH luminosity function $n(L,z)$ at 120~MHz (top left panel) and cumulative
  number density of RHs  $n(>L,z)$ (bottom left panel) at different redshifts $z$ (color
  coded) for the model realization described in Section~\ref{sec:4} with a 10 per cent
  fraction of radio-loud clusters. To obtain an analytical model for $n(L,z)$,
  we fit the logarithm of the RLF at each $z$ with a second-order polynomial and
  constrain the evolution of the three free parameters to follow a linear
  function in $1+z$ (see main text for details). The right panels show the
  comparison of the RLF fits (top) and the cumulative number density of the
  MultiDark samples (bottom) to the constrained analytical model.  \qc{The bottom panels 
  of these two panels show the relative differences $\Delta n / n =
  (n_{\rmn{analytical}} - n_{\rmn{fit}})/n_{\rmn{fit}}$ (top) and
  $\Delta n / n = (n_{\rmn{analytical}} - n_{\rmn{simulation}})/n_{\rmn{simulation}}$ (bottom).} 
  Additionally shown is the LOFAR Tier~1 \emph{point-source} flux limit of
  $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy \citep{2012JApA..tmp...34R} converted to a
  luminosity limit at a given redshift. Horizontal error bars represent the mass
  bins while the vertical error bars are Poissonian uncertainties.  The light
  gray line marked by the arrow estimates the incompleteness limit owing to the
  adopted low-mass cut (in the construction of the mock cluster catalog, see Paper~I)
  and the scatter in the halo luminosities.}
\label{fig:RLF_120}
\end{figure*}

>>>>

\begin{figure*} 
\centering
\includegraphics[width=0.5\textwidth,height=0.305\textheight]{figures/RLF_LOFAR.eps}
\includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/RLF_LOFAR_analytical_1.eps}
\includegraphics[width=0.5\textwidth,height=0.305\textheight]{figures/CumDensityL_LOFAR.eps}
\includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/CumDensityL_LOFAR_1.eps}
\caption{RH luminosity function $n(L,z)$ at 120~MHz (top left panel) and
  cumulative number density of RHs $n(>L,z)$ (bottom left panel) at different
  redshifts $z$ (color coded) for the model realization described in
  Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters. To
  obtain an analytical model for $n(L,z)$, we fit the logarithm of the RLF at
  each $z$ with a second-order polynomial and constrain the evolution of the
  three free parameters to follow a linear function in $1+z$ (see main text for
  details). The right panels show the comparison of the RLF fits (top) and the
  cumulative number density of the MultiDark samples (bottom) to the constrained
  analytical model.  The bottom panels on the right-hand side show the relative
  differences $\Delta n / n = (n_{\rmn{analytical}} -
  n_{\rmn{fit}})/n_{\rmn{fit}}$ (top) and $\Delta n / n = (n_{\rmn{analytical}}
  - n_{\rmn{simulation}})/n_{\rmn{simulation}}$ (bottom).  Additionally shown is
  the LOFAR Tier~1 \emph{point-source} flux limit of
  $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy \citep{2012JApA..tmp...34R} converted to a
  luminosity limit at a given redshift. Horizontal error bars represent the mass
  bins while the vertical error bars are Poissonian uncertainties.  The light
  gray line marked by the arrow estimates the incompleteness limit owing to the
  adopted low-mass cut (in the construction of the mock cluster catalog, see
  Paper~I) and the scatter in the halo luminosities.}
\label{fig:RLF_120}
\end{figure*}
